\vspace{-\baselineskip} Fast and scalable Gaussian process modeling with applications to astronomical time series \vspace{-2\baselineskip}

### 2017-11-13 paper/ms.tex
layout
zenodo links

\newcommand{\response}[1]{{#1}}
\newcommand{\responseb}[1]{{\color{blue}{#1}}}

@@

@@

\edef \simons {\arabic{affilcounter}}\stepcounter{affilcounter}
\altaffiltext{\simons}{Simons Fellow}

\edef \columbia {\arabic{affilcounter}}\stepcounter{affilcounter}
\altaffiltext{\columbia}{Department of Astronomy, Columbia University,
                         New York, NY}

\author{%
    Daniel~Foreman-Mackey\altaffilmark{\sagan,\uw},
    Eric~Agol\altaffilmark{\uw,\guggenheim},
    Sivaram~Ambikasaran\altaffilmark{\iis}, and
    Ruth~Angus\altaffilmark{\simons,\columbia}
}

@@

Our main expertise lies in the field of exoplanet discovery and
characterization where GPs have become a model of choice.
We are confident that this method will benefit this field, but we also expect
that there will be applications in other branches of astrophysics and beyond.
In \sect{examples}, we present applications of the method to research problems
in stellar rotation (\sect{rotation}), asteroseismic analysis (\sect{astero}),
and exoplanet transit fitting (\sect{transit}).
Some readers might consider starting with these section for motivating
examples before delving into the detailed derivations of the earlier sections.

In the following pages, we motivate the general problem of GP modeling, derive
our novel direct solver, and demonstrate the model's application on real and
simulated data sets.
Alongside this paper, we have released well-tested and documented open source
implementations written in \project{C++}, \project{Python}, and
\project{Julia}.
These are available online at \project{GitHub}
\url{https://github.com/dfm/celerite} and \project{Zenodo}
\citep{Foreman-Mackey:2017}.

@@

\newpage
\section{The celerite model}\sectlabel{celerite}

@@

\newpage
\subsection{Scalable computation of celerite models}\sectlabel{scalable}

@@

\subsection{Example 3: Stellar rotation} \sectlabel{rotation}

@@

Alongside this paper, we have released a well-tested and documented open
source software package that implements the method and all of the examples
discussed in these pages.
This software is available on GitHub
\url{https://github.com/dfm/celerite}\footnote{This version of the paper was
generated with git commit \texttt{\githash} (\gitdate).} and Zenodo
\citep{Foreman-Mackey:2017}, and it is made available under the MIT license.

>>>>

\newcommand{\response}[1]{{#1}}
\newcommand{\responseb}[1]{{#1}}

@@

\edef \cca {\arabic{affilcounter}}\stepcounter{affilcounter}
\altaffiltext{\cca}{Center for Computational Astrophysics,
                   Flatiron Institue, New York, NY}

@@

%\edef \simons {\arabic{affilcounter}}\stepcounter{affilcounter}
%\altaffiltext{\simons}{Simons Fellow}

\edef \columbia {\arabic{affilcounter}}\stepcounter{affilcounter}
\altaffiltext{\columbia}{Simons Fellow;
                         Department of Astronomy, Columbia University,
                         New York, NY}

\author{%
    Daniel~Foreman-Mackey\altaffilmark{\sagan,\uw,\cca},
    Eric~Agol\altaffilmark{\uw,\guggenheim},
    Sivaram~Ambikasaran\altaffilmark{\iis}, and
    Ruth~Angus\altaffilmark{\columbia}
}

@@

Our main expertise lies in the field of exoplanet discovery and
characterization where GPs have become a model of choice.
We are confident that this method will benefit this field, but we also expect
that there will be applications in other branches of astrophysics and beyond.
In \sect{examples}, we present applications of the method to research problems
in stellar rotation (\sect{rotation}), asteroseismic analysis (\sect{astero}),
and exoplanet transit fitting (\sect{transit}).
Some readers might consider starting with this section for motivating
examples before delving into the detailed derivations of the earlier sections.

In the following pages, we motivate the general problem of GP modeling, derive
our novel direct solver, and demonstrate the model's application on real and
simulated data sets.
Alongside this paper, we have released well-tested and documented open source
implementations written in \project{C++}, \project{Python}, and
\project{Julia}.
These are available online at \project{GitHub}
\url{https://github.com/dfm/celerite} and
\dataset[Zenodo]{https://doi.org/10.5281/zenodo.806847}.

@@

\section{The celerite model}\sectlabel{celerite}

@@

\subsection{Scalable computation of celerite models}\sectlabel{scalable}

@@

\newpage
\subsection{Example 3: Stellar rotation} \sectlabel{rotation}

@@

Alongside this paper, we have released a well-tested and documented open
source software package that implements the method and all of the examples
discussed in these pages.
This software is available on GitHub
\url{https://github.com/dfm/celerite}\footnote{This version of the paper was
generated with git commit \texttt{\githash} (\gitdate).} and
\dataset[Zenodo]{https://doi.org/10.5281/zenodo.806847}, and it is made
available under the MIT license.
